SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 method.tex
adding method.tex

\noindent \textbf{Global Pearson's Correlation} Here we examine the
perceptron weights at the end of all trace execution by which time the
weights have settled to steady values. The weights obtained from
running all the SPEC CPU 2017 traces are concatenated.  Features with
a bulk of their perceptron weights concentrated around 0 or small
magnitude numbers show a weak correlation with the prefetching
outcome.  On the other hand, features with most of the weights
saturated around highest value (+15) show a high positive correlation
and the features with weights close to the lowest value (-16) show a
strong negative correlation.

@@

\noindent \textbf{Per Trace Correlation} Another important way to look
at the perceptron features is to see how much their contribution
varies across the traces. Here we give special attention to features
with low P-values in. Figure~\ref{Fig:Pvals_Trace} shows the variation
of P-values for three features : \textit{PC XOR Delta},
\textit{Signature XOR Delta} and \textit{PC XOR Depth}; across all the
SPEC CPU 2017 traces.  For simplicity, the traces are arranged in an
increasing order of contribution made by the feature.  It can be seen
that even features with a low overall correlation provide useful
correlation (magnitude > 0.5) for a significant number of traces. This
study motivated us to choose \textit{PC XOR DELTA} over \textit{Last
  Signature} as it provided useful correlation in at least some of the
traces.

\noindent \textbf{Trimming Features Using Cross-correlation} Beside
providing interesting insights into prefetching behavior, P-value can
also be used for feature selection and prefetcher tuning.

>>>>

\noindent \textbf{Global Pearson's Correlation:} Here we examine the
perceptron weights at the end of all trace execution by which time the
weights have settled to steady values. The weights obtained from
running all the SPEC CPU 2017 traces are concatenated.  Features with
a bulk of their perceptron weights concentrated around 0 or small
magnitude numbers show a weak correlation with the prefetching
outcome.  On the other hand, features with most of the weights
saturated around highest value (+15) show a high positive correlation
and the features with weights close to the lowest value (-16) show a
strong negative correlation.

@@

\noindent \textbf{Per Trace Correlation:} Another important way to look
at the perceptron features is to see how much their contribution
varies across the traces. Here we give special attention to features
with low P-values in. Figure~\ref{Fig:Pvals_Trace} shows the variation
of P-values for three features : \textit{PC XOR Delta},
\textit{Signature XOR Delta} and \textit{PC XOR Depth}; across all the
SPEC CPU 2017 traces.  For simplicity, the traces are arranged in an
increasing order of contribution made by the feature.  It can be seen
that even features with a low overall correlation provide useful
correlation (magnitude > 0.5) for a significant number of traces. This
study motivated us to choose \textit{PC XOR DELTA} over \textit{Last
  Signature} as it provided useful correlation in at least some of the
traces.

\noindent \textbf{Trimming Features Using Cross-correlation:} Beside
providing interesting insights into prefetching behavior, P-value can
also be used for feature selection and prefetcher tuning.
